%% The MIT License (MIT)

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Carter Watts}
\address{Berkeley, CA}
%\webpage{www.TODO.com}
\contacts{(706) 905-0412 \linebreak cdwatts2001@gmail.com}
\github{github.com/carterDWatts}

\begin{document}

	% Print the header
	\makeheader
	% Print the content

        \begin{cvsection}{Education}

		\begin{cvsubsection}{University of California Berkeley}{Berkeley, CA}{Aug 2020 -- May 2024}
			\begin{itemize}
				\item \text{B.S. in Electrical Engineering and Computer Science}
                    \item \text{Technical GPA: 3.667}
			\end{itemize}
                \begin{itemize}
				\item \text{Minor in Ancient Greek and Roman Studies}
			\end{itemize}
		\end{cvsubsection}
 %        \begin{cvsubsection}{Columbus High School}{Columbus, GA}{}
	% 		\begin{itemize}
	% 			\item GPA: 4.72, 14 APs + Multivariable Calculus. Robotics - Programming lead and Electrical Team, Math Team, Track, Cross Country, Investment Club, Art Club
	% 		\end{itemize}
	% 	\end{cvsubsection}
  
	\end{cvsection}

	\begin{cvsection}{Employment}

            \begin{cvsubsection}{SWE Intern}{Amazon AWS S3}{May 2023 – Aug 2023}
			%iChat AV			
			\begin{itemize}
            \item Implemented data center cellularization of regional throttling of lifecycle transitions.
            \item Designed new parsing systems for team use of per bucket per cell transition data.
            \item Integrated new throttling system into team's lifecycle action enqueuer to begin use
			\end{itemize}
		\end{cvsubsection}

            \begin{cvsubsection}{Software Engineer}{Pure}{Jan 2023 – May 2022}
			%iChat AV			
			\begin{itemize}
            \item First engineer implementing database solutions and building API connections to apps, web pages, and internal analytics systems through AWS tools and custom internal systems. 
			\end{itemize}
		\end{cvsubsection}
 
		\begin{cvsubsection}{SWE Intern}{Amazon AWS S3}{May 2022 – Aug 2022}
			%iChat AV			
			\begin{itemize}
            \item Implemented data recording systems in Java with storage in DynamoDB on an existing data throttling tool for use in an operator dashboard.
            \item Designed API's for exposure of tracked data using Java and Amazon's Coral structure.
			\item Developed my team's first internal dashboard with TypeScript and React to display data collected from the Throttle Tool and other future tools with intuitive and reliable user interfaces fitting Amazon's style.
			\end{itemize}
		\end{cvsubsection}
  
		\begin{cvsubsection}{Software Engineer}{Ventorlux}{Jun 2019 - Jan 2021}	
			\begin{itemize}
            	\item Biotechnology company focused on removal of pathogens from the air via UV-C radiation. 
                \item Embedded software developer, Embedded electronics developer, Electrical power design for UV-C radiation devices, Front and Back end web developer.
            \end{itemize}
		\end{cvsubsection}

	\end{cvsection}

        \begin{cvsection}{Projects}
		\begin{cvsubsection}{Modular Robot \& Control System}{}{}
			%iChat AV			
			\begin{itemize}
                \item github.com/carterDWatts/miniBot 
                \item Small, modular, tank like, platform robot that receives movement controls via mesh network. Consists of two electrically and programatically separate pods with tank style tread. Programming in C++ and electronic design in AutodesEagle.
			\end{itemize}
		\end{cvsubsection}

            \begin{cvsubsection}{Motion Control System}{}{}
			%iChat AV			
			\begin{itemize}
                \item github.com/carterDWatts/powerGlove
                \item Hand orientation and acceleration based control system that communicates through mesh network and interfaces with multiple devices. Programming in C++ and electronic design in AutodesEagle.
			\end{itemize}
		\end{cvsubsection}

         %    \begin{cvsubsection}{Classic Car Pricing}{}{}
         %        %iChat AV			
         %        \begin{itemize}
         %            \item https://github.com/carterDWatts/price
         %            \item Data collection system with storage in AWS used to create a pricing model for classic cars that utilizes descriptive nonnumerical data.
         %        \end{itemize}
        	% \end{cvsubsection}
         
        \end{cvsection}
    	
        \begin{cvsection}{Relevant Berkeley Classes}
            \begin{cvsubsection}{}{}{}
    			\begin{itemize}

                        \item \textbf{CS 170} Efficient Algorithms and Intractable Problems
                    
    				\item \textbf{CS 188} Introduction to Artificial Intelligence

                        \item \textbf{CS 186} Database Systems

                        \item \textbf{EECS 106A} Robotics
        
    				\item \textbf{CS 70} Discrete Mathematics and Probability Theory
    
    				\item \textbf{CS 61 A-C} Data Structures, The internal organization and operation of digital computers, Machine architecture, Elements of computer logic design.
        
    				\item  \textbf{EECS 16 A-B} Signal processing, learning, control, and circuit design. Linear-algebra. Building modern information devices.
        
    			\end{itemize}
            \end{cvsubsection}
        \end{cvsection}

        \begin{cvsection}{Languages and Technologies}
            \begin{cvsubsection}{}{}{}	
                \begin{itemize}
                    \item Java, Python, C++, C, C\#, Processing, JavaScript, Node.js, HTML, CSS, Git, Arch Linux, Linux, Autodesk Eagle, MongoDB, AWS, S3, RDD, DynamoDB, React, SQL, RISC-V, Assembly, Latex, TypeScript
                \end{itemize}
            \end{cvsubsection}
        \end{cvsection}
	
\end{document}

